Zaca Fire Type Conversion

### 2020-10-09 Model Data Sheets and Code/Manuscript_Code.Rmd
work on combined model

#solar radiation
nlm2 <- plot(FeatureEffect$new(nlm_predictor, feature = "sr")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high2 <- plot(FeatureEffect$new(high_predictor, feature = "sr")) + ggtitle("High") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc2 <- plot(FeatureEffect$new(tc_predictor, feature = "sr")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm2, high2, tc2, nrow=1)
ggsave(here::here("Graph Images", "mcf sr.jpg"))

#precip
nlm3 <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high3 <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("High") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc3 <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))#+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm3, high3, tc3, nrow=1)
ggsave(here::here("Graph Images", "mcf precip.jpg"))

#tmax
nlm4 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmax")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high4 <- plot(FeatureEffect$new(high_predictor, feature = "tmax")) + ggtitle("High") + labs(x="Max August Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc4 <- plot(FeatureEffect$new(tc_predictor, feature = "tmax")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm4, high4, tc4, nrow=1)
ggsave(here::here("Graph Images", "mcf tmax.jpg"))

#tmin jan 2007
nlm5 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmin_jan2007")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
high5 <- plot(FeatureEffect$new(high_predictor, feature = "tmin_jan2007")) + ggtitle("High") + labs(x="Min 2007 January Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc5 <- plot(FeatureEffect$new(tc_predictor, feature = "tmin_jan2007")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm5, high5, tc5, nrow=1)
ggsave(here::here("Graph Images", "mcf tmin_jan2007.jpg"))

#vpd aug
nlm6 <- plot(FeatureEffect$new(nlm_predictor, feature = "vpd_aug")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high6 <- plot(FeatureEffect$new(high_predictor, feature = "vpd_aug")) + ggtitle("High") + labs(x="Max August VPD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc6 <- plot(FeatureEffect$new(tc_predictor, feature = "vpd_aug")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm6, high6, tc6, nrow=1)
ggsave(here::here("Graph Images", "mcf vpd_aug.jpg"))

#cwd
nlm7 <- plot(FeatureEffect$new(nlm_predictor, feature = "cwd")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high7 <- plot(FeatureEffect$new(high_predictor, feature = "cwd")) + ggtitle("High") + labs(x="CWD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc7 <- plot(FeatureEffect$new(tc_predictor, feature = "cwd")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm7, high7, tc7, nrow=1)
ggsave(here::here("Graph Images", "mcf cwd.jpg"))

#evi
nlm8 <- plot(FeatureEffect$new(nlm_predictor, feature = "evi_2006")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high8 <- plot(FeatureEffect$new(high_predictor, feature = "evi_2006")) + ggtitle("High") + labs(x="2006 EVI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc8 <- plot(FeatureEffect$new(tc_predictor, feature = "evi_2006")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm8, high8, tc8, nrow=1)
ggsave(here::here("Graph Images", "mcf evi.jpg"))

#slope
nlm9 <- plot(FeatureEffect$new(nlm_predictor, feature = "slope")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high9 <- plot(FeatureEffect$new(high_predictor, feature = "slope")) + ggtitle("High") + labs(x="Slope")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc9 <- plot(FeatureEffect$new(tc_predictor, feature = "slope")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm9, high9, tc9, nrow=1)
ggsave(here::here("Graph Images", "mcf slope.jpg"))

#tslf
nlm10 <- plot(FeatureEffect$new(nlm_predictor, feature = "tslf")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high10 <- plot(FeatureEffect$new(high_predictor, feature = "tslf")) + ggtitle("High") + labs(x="TSLF")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc10 <- plot(FeatureEffect$new(tc_predictor, feature = "tslf")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm10, high10, tc10, nrow=1)
ggsave(here::here("Graph Images", "mcf tslf.jpg"))

#twi
nlm11 <- plot(FeatureEffect$new(nlm_predictor, feature = "TWI")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high11 <- plot(FeatureEffect$new(high_predictor, feature = "TWI")) + ggtitle("High") + labs(x="TWI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc11 <- plot(FeatureEffect$new(tc_predictor, feature = "TWI")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm11, high11, tc11, nrow=1)
ggsave(here::here("Graph Images", "mcf twi.jpg"))

#aspect
nlm12 <- plot(FeatureEffect$new(nlm_predictor, feature = "aspect_transformed")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high12 <- plot(FeatureEffect$new(high_predictor, feature = "aspect_transformed")) + ggtitle("High") + labs(x="Aspect")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc12 <- plot(FeatureEffect$new(tc_predictor, feature = "aspect_transformed")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) # + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm12, high12, tc12, nrow=1)
ggsave(here::here("Graph Images", "mcf Aspect.jpg"))

@@

d = 7
#ndmi
nlm1 <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high1 <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + themet.margin = unit(c(d,1,1,1), "lines"))
tc1 <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm1, high1, tc1, nrow=1)
##ggsave(here::here("Graph Images", "mcf ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

#solar radiation
nlm2 <- plot(FeatureEffect$new(nlm_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
high2 <- plot(FeatureEffect$new(high_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ themet.margin = unit(c(d,1,1,1), "lines"))
tc2 <- plot(FeatureEffect$new(tc_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))#+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
##ggsave(here::here("Graph Images", "mcf sr.jpg"))

#precip
nlm3 <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
high3 <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2))#+ themet.margin = unit(c(d,1,1,1), "lines"))
tc3 <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2))#+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
##ggsave(here::here("Graph Images", "mcf precip.jpg"))

#evi
nlm4 <- plot(FeatureEffect$new(nlm_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
high4 <- plot(FeatureEffect$new(high_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
tc4 <- plot(FeatureEffect$new(tc_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf evi.jpg"))

#tmax
nlm5 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
high5 <- plot(FeatureEffect$new(high_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
tc5 <- plot(FeatureEffect$new(tc_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf tmax.jpg"))

#tmin jan 2007
nlm6 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
high6 <- plot(FeatureEffect$new(high_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
tc6 <- plot(FeatureEffect$new(tc_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ themet.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf tmin_jan2007.jpg"))

#vpd aug
nlm7 <- plot(FeatureEffect$new(nlm_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))# + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high7 <- plot(FeatureEffect$new(high_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))# + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc7 <- plot(FeatureEffect$new(tc_predictor, feature = "vpd_aug")) + ggtitle("") + labs(x="Max August VPD")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) #+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm7, high7, tc7, nrow=1)
#ggsave(here::here("Graph Images", "mcf vpd_aug.jpg"))

>>>>

#solar radiation
nlm2 <- plot(FeatureEffect$new(nlm_predictor, feature = "sr")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high2 <- plot(FeatureEffect$new(high_predictor, feature = "sr")) + ggtitle("High") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc2 <- plot(FeatureEffect$new(tc_predictor, feature = "sr")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm2, high2, tc2, nrow=1)
ggsave(here::here("Graph Images", "mcf sr.jpg"))

#precip
nlm3 <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("ULM") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high3 <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("High") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc3 <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("Type Converted") + labs(x="") + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm3, high3, tc3, nrow=1)
ggsave(here::here("Graph Images", "mcf precip.jpg"))

#tmax

#tmin jan 2007
nlm5 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmin_jan2007")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high5 <- plot(FeatureEffect$new(high_predictor, feature = "tmin_jan2007")) + ggtitle("High") + labs(x="Min 2007 January Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc5 <- plot(FeatureEffect$new(tc_predictor, feature = "tmin_jan2007")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm5, high5, tc5, nrow=1)
ggsave(here::here("Graph Images", "mcf tmin_jan2007.jpg"))

#vpd aug
nlm6 <- plot(FeatureEffect$new(nlm_predictor, feature = "vpd_aug")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high6 <- plot(FeatureEffect$new(high_predictor, feature = "vpd_aug")) + ggtitle("High") + labs(x="Max August VPD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc6 <- plot(FeatureEffect$new(tc_predictor, feature = "vpd_aug")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm6, high6, tc6, nrow=1)
ggsave(here::here("Graph Images", "mcf vpd_aug.jpg"))

#cwd
nlm7 <- plot(FeatureEffect$new(nlm_predictor, feature = "cwd")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high7 <- plot(FeatureEffect$new(high_predictor, feature = "cwd")) + ggtitle("High") + labs(x="CWD")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc7 <- plot(FeatureEffect$new(tc_predictor, feature = "cwd")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm7, high7, tc7, nrow=1)
ggsave(here::here("Graph Images", "mcf cwd.jpg"))

#evi
nlm8 <- plot(FeatureEffect$new(nlm_predictor, feature = "evi_2006")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high8 <- plot(FeatureEffect$new(high_predictor, feature = "evi_2006")) + ggtitle("High") + labs(x="2006 EVI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc8 <- plot(FeatureEffect$new(tc_predictor, feature = "evi_2006")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm8, high8, tc8, nrow=1)
ggsave(here::here("Graph Images", "mcf evi.jpg"))

#slope
nlm9 <- plot(FeatureEffect$new(nlm_predictor, feature = "slope")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high9 <- plot(FeatureEffect$new(high_predictor, feature = "slope")) + ggtitle("High") + labs(x="Slope")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc9 <- plot(FeatureEffect$new(tc_predictor, feature = "slope")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm9, high9, tc9, nrow=1)
ggsave(here::here("Graph Images", "mcf slope.jpg"))

#tslf
nlm10 <- plot(FeatureEffect$new(nlm_predictor, feature = "tslf")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high10 <- plot(FeatureEffect$new(high_predictor, feature = "tslf")) + ggtitle("High") + labs(x="TSLF")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc10 <- plot(FeatureEffect$new(tc_predictor, feature = "tslf")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm10, high10, tc10, nrow=1)
ggsave(here::here("Graph Images", "mcf tslf.jpg"))

#twi
nlm11 <- plot(FeatureEffect$new(nlm_predictor, feature = "TWI")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high11 <- plot(FeatureEffect$new(high_predictor, feature = "TWI")) + ggtitle("High") + labs(x="TWI")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc11 <- plot(FeatureEffect$new(tc_predictor, feature = "TWI")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm11, high11, tc11, nrow=1)
ggsave(here::here("Graph Images", "mcf twi.jpg"))

#aspect
nlm12 <- plot(FeatureEffect$new(nlm_predictor, feature = "aspect_transformed")) + ggtitle("ULM") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))  + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high12 <- plot(FeatureEffect$new(high_predictor, feature = "aspect_transformed")) + ggtitle("High") + labs(x="Aspect")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))  + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc12 <- plot(FeatureEffect$new(tc_predictor, feature = "aspect_transformed")) + ggtitle("Type Converted") + labs(x="")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2))  + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm12, high12, tc12, nrow=1)
ggsave(here::here("Graph Images", "mcf Aspect.jpg"))

@@

d = 7
#ndmi
nlm1 <- plot(FeatureEffect$new(nlm_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high1 <- plot(FeatureEffect$new(high_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc1 <- plot(FeatureEffect$new(tc_predictor, feature = "ndmi_2006")) + ggtitle("") + labs(x="NDMI 2006") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm1, high1, tc1, nrow=1)
##ggsave(here::here("Graph Images", "mcf ndmi.jpg"))
#theme (panel.background = element_rect(width = 5))

#solar radiation
nlm2 <- plot(FeatureEffect$new(nlm_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high2 <- plot(FeatureEffect$new(high_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc2 <- plot(FeatureEffect$new(tc_predictor, feature = "sr")) + ggtitle("") + labs(x="Solar Radiation") + theme_classic() + scale_y_continuous(lim = c(-0.15, 0.2)) +  theme(axis.text.x = element_text(angle = 15, hjust = 0.85))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
##ggsave(here::here("Graph Images", "mcf sr.jpg"))

#precip
nlm3 <- plot(FeatureEffect$new(nlm_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high3 <- plot(FeatureEffect$new(high_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc3 <- plot(FeatureEffect$new(tc_predictor, feature = "rain")) + ggtitle("") + labs(x="Annual Precipitation") + theme_classic() + scale_y_continuous(lim = c(-0.2,0.2))+ theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
##ggsave(here::here("Graph Images", "mcf precip.jpg"))

#evi
nlm4 <- plot(FeatureEffect$new(nlm_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high4 <- plot(FeatureEffect$new(high_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc4 <- plot(FeatureEffect$new(tc_predictor, feature = "evi_2006")) + ggtitle("") + labs(x="EVI 2006")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf evi.jpg"))

#tmax
nlm5 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high5 <- plot(FeatureEffect$new(high_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc5 <- plot(FeatureEffect$new(tc_predictor, feature = "tmax")) + ggtitle("") + labs(x="Max August Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf tmax.jpg"))

#tmin jan 2007
nlm6 <- plot(FeatureEffect$new(nlm_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
high6 <- plot(FeatureEffect$new(high_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")+ theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
tc6 <- plot(FeatureEffect$new(tc_predictor, feature = "tmin_jan2007")) + ggtitle("") + labs(x="Min 2007 Jan Temp")  + theme_classic() + scale_y_continuous(lim = c(-0.15,0.2)) + theme(plot.margin = unit(c(d,1,1,1), "lines"))
ggarrange(nlm, high, tc, nrow=1)
#ggsave(here::here("Graph Images", "mcf tmin_jan2007.jpg"))
